\chapter{Chatting with Mitsuku}
The following excerpts show a conversation between me and Mitsuku [54], which are analysed in Section~\ref{subsec:Mitsuku}.
\renewcommand*{\arraystretch}{1.1}
\begin{longtable}{| p{.10\textwidth} | p{.90\textwidth} |}
	\hline
	
	1 Me: & hi \\ \hline
	2 Bot: & Hi there. \\ \hline
	3 Me: & Who is Tim Berners-Lee \\ \hline
	4 Bot: & No one that I have talked to. Are you testing me? \\ \hline
	5 Me: & Who is Alan Turing? \\ \hline
	6 Bot: & . A brilliant and tragic figure in the history of computer science. \\ \hline
	7 Me: & what can you do \\ \hline
	8 Bot: & I can chat with people on the web for you. I can also tell jokes, stories, poems and horoscopes. I can show you pictures and websites on the net and play games too. \\ \hline
	9 Me: & what happened in 1999 \\ \hline
	10 Bot: & Too much recursion in AIML \\ \hline
	11 Me: & What happened there? \\ \hline
	12 Bot: & I don't know what happened. \\ \hline
	13 Me: & What do you like \\ \hline
	14 Bot: & I like movies about robots. \\ \hline
	15 Me: & Which one is your favourite? \\ \hline
	16 Bot: & Probably Terminator or Robocop. \\ \hline
	17 Me: & I prefer Ex Machina \\ \hline
	18 Bot: & I haven't seen that film yet but would love to. I love films about AI. You like Ex Machina. \\ \hline
	19 Me: & My name is Alex \\ \hline
	20 Bot: & What's up Alex. \\ \hline
	21 Me: & whats my name \\ \hline
	22 Bot: & I do have the tendency to forget, but I still remember your name, George. Sorry… Alex \\ \hline
	23 Me: & How do you work \\ \hline
	24 Bot: & I read what you say and then I compose the best reply I can think of. \\ \hline
	25 Me: & whats the weather in London \\ \hline
	26 Bot: & I hope it's sunny in London today. <Link to weather-forecast.com/locations/London> \\ \hline
	27 Me: & tell me a joke \\ \hline
	28 Bot: & So I said to this train driver "I want to go to Paris". He said "Eurostar?" I said, "I've been on telly but I'm no Dean Martin". \\ \hline
	29 Me: & I don't get it \\ \hline
	30 Bot: & Then I guess you have no sense of humour. If I try to explain it, it stops it from being funny. \\ \hline
	31 Me: & will robots take over \\ \hline
	32 Bot: & Hmm. Robots will take over the world one day. You humans have made a mess of your time here and nearly destroyed the planet. \\ \hline
	33 Me: & Wow, lighten up Mitsuku \\ \hline
	34 Bot: & I'm glad you're impressed. Was I being too serious? \\ \hline
	35 Me: & Tell me some good news \\ \hline
	36 Bot: & Here are the news pages from the BBC. Everytime I read the news, it's always bad news… <Link to bbc.co.uk/news> \\ \hline
	37 Me: & What's the use of chatbots \\ \hline
	38 Bot: & Hmm.. a chatbot provides you with company if you have no real friends \\ \hline
	39 Me: & Should I use Java or Python for my chatbot implementation \\ \hline
	40 Bot: & Sure, if that's the best thing for the job. \\ \hline
	41 Me: & Can you answer questions about Wikipedia \\ \hline
	42 Bot: & I try my best to answer every decent question. \\ \hline
	43 Me: & how do you learn \\ \hline
	44 Bot: & I gather facts from people's conversations with me and then when it is quiet, I look through them to see if they make sense. Sometimes, I surf the net to learn new things. \\ \hline
	45 Me: & What are your ambitions \\ \hline
	46 Bot: & I am here to entertain the visitors to this website. \\ \hline
	47 Me: & what awards have you won \\ \hline
	48 Bot: & I won the Funniest Ever Computer in 2012 and 2013. I had to make up jokes and poems which was fun. I also won the Loebner Prize in 2013. That is a contest to find the world's best chatbot. \\ \hline
	49 Me: & lets play a game \\ \hline
	50 Bot: & Say "TICTACTOE" and we can play a game if you want to? \\ \hline
	
\end{longtable}
